\documentclass[12pt]{report}
\usepackage[english]{babel}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\rhead{}
\rhead{Design Project \\ Articles Summaries}
\lhead{Titouan Vervack \\ Stefaan Vermassen}

\begin{document}
T21: 2, 4, 7, 11, 14, 20, hillier (13 in reference paper)
\subsubsection*{1. Hildebrand D. On the capacity of tandem server, finite queue, service systems. Operations Research 1968.}
% http://www.jstor.org/stable/168403?seq=1
\subsubsection*{2. Smith JM. Cruz FRB. van Woensel T. Topological network design of general, finite, multi-server queueing networks. Plos One. 2010.}
% http://www.sciencedirect.com/science/article/pii/S0377221709001489
\subsubsection*{3. Smith JM. Cruz FRB. van Woensel T. Topological network design of general, finite, multi-server queueing networks. Plos One. 2010.}
% http://www.sciencedirect.com/science/article/pii/0305054894900922
\subsubsection*{4. Cruz FRB. Van Woensel T. Smith JM. Buffer and throughput trade-offs in M/G/1/K queueing networks: A bi-criteria approach. International Journal of Production Economics 2010.}
% http://www.sciencedirect.com/science/article/pii/S0925527310000836
\subsubsection*{5. Smith JM. System capacity and performance modelling of finite buffer queueing networks. International Journal Of Production Research 2014.}
% http://phdtree.org/pdf/41297998-system-capacity-and-performance-modelling-of-finite-buffer-queueing-networks/
\subsubsection*{6. Hillier FS. Kut C. The assignment of extra servers to stations in Tandem Queueing systems with small or no buffers. Performance Evaluation 1989.}
% http://www.sciencedirect.com/science/article/pii/0166531689900126
\subsubsection*{7. Hillier F, Boling R. Finite queues in series with exponential or Erlang service
times: a numerical approach. Operations Research 1967;16:286–303.}
% http://web.a.ebscohost.com/ehost/pdfviewer/pdfviewer?sid=d877a955-5433-4b9d-8522-323f9f9d4a32%40sessionmgr4005&vid=1&hid=4204
Met buffer, 1 server, N knopen, tandem, BAS, exponential distribution (of Erlang distribution?)
\end{document}